[dcpo_demsupport] Appendix

### 2020-07-12 paper/dcpo_demsupport_appendix.Rmd
clean up; use here::here for claassen_input

```{r claassen_input_raw}
claassen_input_raw <- DCPOtools:::claassen_setup(vars = read_csv("data-raw/mood_dem.csv",
                                                                 col_types = "ccccc"),
                                       file = "data/claassen_input_raw.csv")
```

@@

claassen_input_cy <- read_csv("data/claassen_input_raw.csv",
                              col_types = "cdcddcd") %>%           # 1784 obs
    mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
           project = case_when(p_dcpo == "afrob" ~ "afb",
                               p_dcpo == "amb" ~ "lapop",
                               p_dcpo == "arabb" ~ "arb",
                               p_dcpo == "asiab" ~ "asb",
                               p_dcpo == "asianb" ~ "asnb",
                               p_dcpo == "neb" ~ "ndb",
                               p_dcpo == "sasianb" ~ "sab",
                               TRUE ~ p_dcpo),
           y_dcpo = year) %>%
    dplyr::select(country, year, y_dcpo, survey, project) %>% 
    unique()

@@

available <- anti_join(claassen_input_cy, supdem_cy)                # 487 obs

@@

cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 398 obs
    select(-y_dcpo)

>>>>

```{r claassen_input}
dcpo_input_raw1 <- read_csv("data/dcpo_input_raw.csv", col_types = "cdcddcd") %>% 
  filter(!(str_detect(survey, "army_wvs") & # WVS obs identified as problematic by Claassen 
                 ((country=="Albania" & year==1998) |
                      (country=="Indonesia" & (year==2001 | year==2006)) |
                      (country=="Iran" & year==2000) |
                      (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                      (country=="Vietnam" & year==2001)) |
                 (str_detect(item, "strong_wvs") &
                      ((country=="Egypt" & year==2012) |
                           (country=="Iran" & (year==2000 | year==2007)) | # 2005 in Claassen
                           (country=="India") |
                           (country=="Pakistan" & (year==1997 | year==2001)) | # 1996 in Claassen
                           (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
                           (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
                           (country=="Vietnam" & year==2001))) |
                 (country %in% c("Puerto Rico", "Northern Ireland", 
                                 "SrpSka Republic", "Hong Kong SAR China")))) %>%
  with_min_yrs(2)

claassen_input <- DCPOtools::format_claassen(dcpo_input_raw1)
save(claassen_input, file = here::here("data", "claassen_input.rda"))
```

@@

claassen_input_cy <- read_csv("data/dcpo_input_raw.csv",
                              col_types = "cdcddcd") %>%           # 1813 obs
  mutate(p_dcpo = str_extract(survey, "^[a-z]+"), 
         project = case_when(p_dcpo == "afrob" ~ "afb",
                             p_dcpo == "amb" ~ "lapop",
                             p_dcpo == "arabb" ~ "arb",
                             p_dcpo == "asiab" ~ "asb",
                             p_dcpo == "asianb" ~ "asnb",
                             p_dcpo == "neb" ~ "ndb",
                             p_dcpo == "sasianb" ~ "sab",
                             TRUE ~ p_dcpo),
         y_dcpo = year) %>%
  dplyr::select(country, year, y_dcpo, survey, project) %>% 
  unique()

@@

available <- anti_join(claassen_input_cy, supdem_cy)                # 516 obs

@@

cys_to_drop <- anti_join(available, year_fixes, by = c("country", "year" = "year.y", "project")) %>% # 427 obs
    select(-y_dcpo)
